MCC Models

### 2019-06-21 papers/full_paper/SI_appendix.Rmd
add numerical example for model

\begin{equation} 
P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P_(r)
\end{equation}

@@

>>>>

\begin{equation} 
P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P(r)
\end{equation}

@@

### Numerical Example

Prior = 0.6416667
SO = 2.242435

\begin{equation} 
Informativity(u; r) = ln P(r|u) \propto ln \sum_L P(r,l|u) P(L) \propto P(r) L_{lit}
Informativity(u; r_1) = ln(0.6416667 * 1) = -0.4436863
Informativity(u; r_1) = ln(0.3583333 * 1) = -1.026292
\end{equation}

(For the above, I get the same results from the model if get these values from webppl)

\begin{equation} 
P_{S_1}(u|r)\propto exp(\alpha Informativity(u;r))
P_{S_1}(u|r_1) = exp(2.242435 * -0.4436863)/(exp(2.242435 * -0.4436863)+exp(2.242435 * -1.026292)) = 0.7869194
P_{S_1}(u|r_2) = exp(2.242435 * -1.026292)/(exp(2.242435 * -0.4436863)+exp(2.242435 * -1.026292)) = 0.2130806
\end{equation}

\begin{equation} 
P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P(r)
P_{L_1}(r_1,L|u) = 0.7869194 * 0.6416667 /(0.7869194 * 0.6416667+0.2130806 * 0.3583333) = 0.8686484
\end{equation}

Result should be: 0.9077334746997058
